Tulai

### 2023-10-27 paper/paper.qmd
stash

A permutation MANOVA indicates that there is a significant difference in the lithic assemblage composition across the three excavation areas (`rPerMANOVA_results_inline`). We investigated this further using pairwise post-hoc tests and found that this significant difference is between TA and TP1, with the other two areas being statisically indistinguishable (@tbl-permanova )

>>>>

A permutation MANOVA indicates that there is a significant difference in the lithic assemblage composition across the three excavation areas (`r PerMANOVA_results_inline`). We investigated this further using pairwise post-hoc tests and found that this significant difference is between TA and TP1, with the other two areas being statisically indistinguishable (@tbl-permanova )
